---
title: "DesignProject"
author: "Michelle Nesbit"
date: "2022-11-16"
output:
  word_document: default
  html_document: default
---
2^4 factorial experimental design
beyblades
A) stadium (a surface it spins on) (grey is low, blue is high)
B) launcher (ripcord tool that starts it spinning) (white is low, black is high)
C) beyblade (spinning top toy) (dark red is low, light red is high)
D) mode (mode 1 is low, mode 2 is high)

We are confounding ABCD interaction within blocks, so that L = x1+x2+x3+x4 (mod 2)
will be 0 if {x1,x2,x3,x4} contains 0, 2, or 4 ones: (1), ab, ac, ad, bc, bd,
cd, abcd, and 1 otherwise

randomize draws
enter data
check dfs
visually look for significant factors
reduce model
run anova
check model assumptions
post hoc?
additional research that could be done?

We need to randomize runs within the blocks

```{r}
#ABCD-:(1), ab, ab, bc, ad, bd, cd, abcd  
#ABCD+: a, b , c, abc, d, abd, acd, bcd
Bl1 <- c('(1)', 'ab', 'ac', 'bc', 'ad', 'bd', 'cd', 'abcd')
Bl2<- c('a', 'b' , 'c', 'abc', 'd', 'abd', 'acd', 'bcd')

#randomly sample from each block
set.seed(2022)
block1_runs <- sample(Bl1,size=8,replace=F)
#bc, ac, bd, cd, abcd, ab, (1), ad
set.seed(2022)
block2_runs <- sample(Bl2,size=8,replace=F)
#abc, c, abd, acd, bcd, b, a, d

#set up experiment
A <- rep(c(-1,1), times=8)
B <- rep(c(-1,1), each = 2, times=4)
C <- rep(c(-1,1), each = 4, times=2)
D <- rep(c(-1,1), each = 8)

#input data
y <- c(24.77, 69.87, 24.04, 98.16, 54.51, 24, 75.72, 4.31, 62.98, 23.98, 83.58, 
       83.8, 31.34, 69.39, 81.41, 108.11)

ABCD <- A*B*C*D #we want to confound

A <- as.factor(A)
B <- as.factor(B)
C <- as.factor(C)
D <- as.factor(D)

beydata <- data.frame(A, B, C, D, ABCD, y)

beymod <- lm(y ~ ((A+B+C+D)^4), data=beydata)
anova(beymod) #not enough df's to do anova so we will visualize and see what effects are significant!

#Visualize effects 
beymod$effects
beymod.effects <- abs(beymod$effects[-1])

qq <- qqnorm(beymod.effects, type="n")  
text(qq$x, qq$y, labels = names(beymod$effects))

# create reduced model by dropping highest order interaction
Blocks <- ABCD
beymod2 <- lm(y ~ A + B + C + D + B*C + C*D + A*B+ B*D + Blocks, data=beydata)
anova(beymod2) 

# We find nothing to be significant factors. Will remove A:B and B:C because they are very insignificant and rerun ANOVA.
beymod3<-lm(y ~ A + B + C + D + C*D + B*D + Blocks, data=beydata)
anova(beymod3) #nothing is significant

#remove A because p value 0.75 and not in any interaction terms
beymod4<-lm(y ~ B + C + D + C*D + B*D + Blocks, data=beydata)
anova(beymod4) #nothing is significant

#remove interaction terms because nothing is significant
beymod5<-lm(y ~ B + C + D + Blocks, data=beydata)
anova(beymod5) #nothing is significant

#remove c because it is not significant
beymod6<-lm(y ~ B + D + Blocks, data=beydata)
anova(beymod6) #nothing is significant

#remove D because it is not significant
beymod7<-lm(y ~ B + Blocks, data=beydata)
anova(beymod7) #nothing is significant!!!! at all!!!!

#model to check for normality
beymod8 <- lm(y ~ A + B + C + D + Blocks, data=beydata)
anova(beymod8)
#effect estimates
beymod8$coefficients

# assumption tests
# residual analysis via normal plot: looks mostly normal, some head/tail
par(mfrow=c(1,2))
qqnorm(beymod8$residuals)
qqline(beymod8$residuals) #this looks pretty normal!! great
#testing assumptions
# we fail to reject normality or homoscedasticity of any main factors
shapiro.test(beymod8$residuals) #hip hip hooray it is normal!
bartlett.test(beymod8$residuals~A) #homoscedastic
bartlett.test(beymod8$residuals~B) #homoscedastic
bartlett.test(beymod8$residuals~C) #homoscedastic
bartlett.test(beymod8$residuals~D) #homoscedastic

#additional analysis
new_y <- ifelse(y > 60, 1, 0)
log_reg <- glm(factor(new_y) ~ factor(A) + factor(B) + factor(C) + factor(D), family="binomial")
summary(log_reg)

```




```{r}

```




```{r}

```

